---
title: "CaseStudy"
runtime: shiny
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, results= 'hide')
```

### Summersemester 2020

```{r, message=FALSE}
library(dplyr)
library(tidyverse)
```

### 1. Data import

The first step is to identify the relevant data sets and to import them into R. This case study is about the control units T2. Therefore, the parts list "Einzelteil_T02" is imported. It contains one or multiple whitespaces as seperatorsand tabs as delimiter between rows. Therefore, read.table is used because it takes one or more whitespaces as sperator. The tabs are replaced with line breaks by the function gsub which is performed on the original data set imported as text by the function readLines.

```{r,results='markup'}
t02 <- read.table(text = gsub("\t", "\n", readLines('./Data/Einzelteil/Einzelteil_T02.txt')))
```

In the next step, the relevant component data is imported. The parts "T2" are built into motors. Thus, the motor components K1BE1, K1BE2, K1DI1, and K1DI2 are the only components which include "T2" parts. The csv files can be imported with the function read.csv and read.csv, depending on whether the seperator is a comma or a semicolon. Data set K1DI1 must be imported the same way as T02 because it has a similar structure. *Maybe not import K1BE2 and K1DI2 because they are not part in vehicles from manufacturer OEM1. Maybe only import bestand, depends on whether the "Fehlerhaft" is important later.*

```{r,results='markup'}
bestand_k1be1 <- read.csv2(row.names = 1, './Data/Komponente/Bestandteile_Komponente_K1BE1.csv')
bestand_k1be2 <- read.csv2(row.names = 1, './Data/Komponente/Bestandteile_Komponente_K1BE2.csv')
bestand_k1di1 <- read.csv2(row.names = 1, './Data/Komponente/Bestandteile_Komponente_K1DI1.csv')
bestand_k1di2 <- read.csv2(row.names = 1, './Data/Komponente/Bestandteile_Komponente_K1DI2.csv')
k1be1 <- read.csv(row.names = 1, './Data/Komponente/Komponente_K1BE1.csv')
k1be2 <- read.csv2(row.names = 1, './Data/Komponente/Komponente_K1BE2.csv')
k1di1 <- read.csv(row.names = 1, './Data/Komponente/Komponente_K1DI1.csv')
k1di2 <- read.table(sep = "\\", text = gsub("\t", "\n", readLines('./Data/Komponente/Komponente_K1DI2.txt')))
```

Additionally, the relevant vehicle data must be imported. Only the vehicles of type 11 and type 12 are relevant for this case study. They are also CSV-files seperated by comma (read.csv) or semicolon (Read.csv2).

```{r,results='markup'}
bestand_fzg_oem1_typ11 <- read.csv2(row.names = 1, './Data/Fahrzeug/Bestandteile_Fahrzeuge_OEM1_Typ11.csv')
bestand_fzg_oem1_typ12 <- read.csv2(row.names = 1, './Data/Fahrzeug/Bestandteile_Fahrzeuge_OEM1_Typ12.csv')
fzg_oem1_typ11 <- read.csv(row.names = 1, './Data/Fahrzeug/Fahrzeuge_OEM1_Typ11.csv')
fzg_oem1_typ12 <- read.csv2(row.names = 1, './Data/Fahrzeug/Fahrzeuge_OEM1_Typ12.csv')
```

The last necessary data set is the one that contains information about the registration of the vehicles. The data is a CSV-file seperated by semicolons.

```{r,results='markup'}
zulassungen <- read.csv2(row.names = 1, './Data/Zulassungen/Zulassungen_alle_Fahrzeuge.csv')
```

### 1. Data preperation

The next step is to prepare the data. Therefore, the data has to be formatted in accordance to the principles of tidy data.

The data frame "t02" contains each colum (except for the row names *maybe add row_names = 1 to t02 import*) twice. Once with suffic x and once with suffix y. The following filter shows that no row contains an ID in both parts:

```{r,results='markup'}
t02 %>%
  filter(is.na(ID_T02.x) & is.na(ID_T02.y))
```

Thus, we can unite each two columns without losing relevant information. The suffix x and y determines which Hersteller built the part but this information is stored in the Herstellernummer and not lost by the merge of the columns. The NAs can be removed.

```{r,results='markup'}
t02 <- t02 %>%
  unite("ID_T02",ID_T02.x,ID_T02.y, na.rm = TRUE) %>%
  unite("Produktionsdatum",Produktionsdatum.x,Produktionsdatum.y, na.rm = TRUE) %>%
  unite("Herstellernummer",Herstellernummer.x,Herstellernummer.y, na.rm = TRUE) %>%
  unite("Werksnummer",Werksnummer.x,Werksnummer.y, na.rm = TRUE) %>%
  unite("Fehlerhaft",Fehlerhaft.x,Fehlerhaft.y, na.rm = TRUE) %>%
  unite("Fehlerhaft_Datum",Fehlerhaft_Datum.x,Fehlerhaft_Datum.y, na.rm = TRUE) %>%
  unite("Fehlerhaft_Fahrleistung",Fehlerhaft_Fahrleistung.x,Fehlerhaft_Fahrleistung.y, na.rm = TRUE)
```

After this, all variables are classfied as characters. In the next step we change them into the formats that fit to the data. This step has to be done on other data again, so a function is created to automate this process.

```{r,results='markup'}
set_formats <- function(x){
  x %>% mutate(
    Produktionsdatum = as.Date(Produktionsdatum),
    Herstellernummer = as.factor(Herstellernummer),
    Werksnummer = as.factor(Werksnummer),
    Fehlerhaft = as.factor(Fehlerhaft),
    Fehlerhaft_Datum = as.Date(Fehlerhaft_Datum),
    Fehlerhaft_Fahrleistung = as.numeric(Fehlerhaft_Fahrleistung)
  )
}
```

The function is applied to "t02".

```{r,results='markup'}
t02 <- set_formats(t02)
```

The dataset "t02" will later be filtered to find the affected parts. Therefore, the last part of its IDs must be copied into a new variable. It is called "ID_number".

```{r,results='markup'}
t02 <- mutate(t02,ID_number = as.integer(gsub("^.*-", "", ID_T02)))
```

The component data must be put in a tidy format as well. Data set K1DI1 has the same columns for x, y and without an index. The following filters show that each object has only a value in one of the three ID columns.

```{r,results='markup'}
k1di1 %>%
  filter(is.na(ID_Motor.x) & is.na(ID_Motor.y) & is.na(ID_Motor))
k1di1 %>%
  filter(!is.na(ID_Motor.x) & !is.na(ID_Motor.y))
k1di1 %>%
  filter(!is.na(ID_Motor.x) & !is.na(ID_Motor))
k1di1 %>%
  filter(!is.na(ID_Motor) & !is.na(ID_Motor.y))
```

Therefore, the three columns of each kind can be united as one, and the NA values can be removed:

```{r,results='markup'}
k1di1 <- k1di1 %>%
  unite("ID_Motor",ID_Motor,ID_Motor.x,ID_Motor.y, na.rm = TRUE) %>%
  unite("Produktionsdatum",Produktionsdatum,Produktionsdatum.x,Produktionsdatum.y, na.rm = TRUE) %>%
  unite("Herstellernummer",Herstellernummer,Herstellernummer.x,Herstellernummer.y, na.rm = TRUE) %>%
  unite("Werksnummer",Werksnummer,Werksnummer.x,Werksnummer.y, na.rm = TRUE) %>%
  unite("Fehlerhaft",Fehlerhaft,Fehlerhaft.x,Fehlerhaft.y, na.rm = TRUE) %>%
  unite("Fehlerhaft_Datum",Fehlerhaft_Datum,Fehlerhaft_Datum.x,Fehlerhaft_Datum.y, na.rm = TRUE) %>%
  unite("Fehlerhaft_Fahrleistung",Fehlerhaft_Fahrleistung,Fehlerhaft_Fahrleistung.x,Fehlerhaft_Fahrleistung.y, na.rm = TRUE)
```

The datasets K1BE1, K1BE2, and K1DI2 contain the columns "Produktionsdatum_Origin_01011970" and "origin" but they seem to be mixed up. In the following step this is corrected (*Produktionsdatum has still some mistakes in it (i.e. 0001 instead of 2001) but we dont need it anyway I think.. shall we keep that step in the script, although we do not need the attributes?.. otherwise we would also have to correct a mistake in the Produktionsdatum column and change origin to factors.*)

```{r,results='markup'}
k1be1 <- k1be1 %>% rename(Produktionsdatum=origin,Origin=Produktionsdatum_Origin_01011970)
k1be2 <- k1be2 %>% rename(Produktionsdatum=origin,Origin=Produktionsdatum_Origin_01011970)
k1di2 <- k1di2 %>% rename(Produktionsdatum=origin,Origin=Produktionsdatum_Origin_01011970)
```

All four data sets of components have their variables as characters now. This is changed with the function set_formats.

```{r,results='markup'}
k1be1 <- set_formats(k1be1)
k1be2 <- set_formats(k1be2)
k1di1 <- set_formats(k1di1)
k1di2 <- set_formats(k1di2)
```

Unfortuantely, this did not work for data set K1DI1 because it contains empty strings in "Fehlerhaft_Datum". Therefore, these empty strings are replaced by NAs. Afterwards, the function set_formats can be applied correctly.

```{r,results='markup'}
k1di1 <- k1di1 %>%
  mutate(Fehlerhaft_Datum = if_else(Fehlerhaft_Datum == "",NA_character_ ,Fehlerhaft_Datum))

k1di1 <- set_formats(k1di1)
```

For the data frames that contain the stock (bestand) of the components, only column 2, and 5 are relevant because the other columns contain IDs of parts which are not T2. They are removed.

```{r,results='markup'}
bestand_k1be1[c(1,3:4)] <- list(NULL)
bestand_k1be2[c(1,3:4)] <- list(NULL)
bestand_k1di1[c(1,3:4)] <- list(NULL)
bestand_k1di2[c(1,3:4)] <- list(NULL)
```


The same can be done for all columns in the stock (bestand) of the vehicles which do not contain the vehicle ID or the motor ID, because all affected components are motors.

```{r,results='markup'}
bestand_fzg_oem1_typ11[c(1:3)] <- list(NULL)
bestand_fzg_oem1_typ12[c(1:3)] <- list(NULL)
```

The next data frame which needs to be tidied up is "zulassungen". It contains a column "Zulassungen" which states the date of the registration of the vehicle. This variable miust be put into a Date format.

```{r,results='markup'}
zulassungen <- zulassungen %>%
  mutate(Zulassung = as.Date(Zulassung))
```

### 3. Creation of final detaset

In the third part, the final datset is created. First of all, we need to filter the data of "to2" to get a dat frame that only contains the affected parts. These parts are either produced by control unit manufacturer "202" in plant "2022" in the period from 31.04.2009 to 31.11.2014 or produced by control unit manufacturere 201 with the production numbers "2-201-2011-1250" to "2-201-2011-19500.

```{r,results='markup'}
t02_affected <- t02 %>%
  filter((Herstellernummer == 202 & Werksnummer == 2022 & Produktionsdatum >= "2009-04-30" & Produktionsdatum <= "2014-11-30") | (Herstellernummer == 201 & Werksnummer == 2011 & ID_number >= 1250 & ID_number <= 19500))
```

In the next step, the list of affected parts is joined with the list of components to assign each affected part to the component in which it is used. Therefore, we only need the ID of the affected parts. These IDs are joined by left_join to all four component sets. (*Maybe keep "Fehlerhaft" information in it too because we will need it in the final dataset as well, I think. Maybe we should then also add suffix to Fehlerhaft (join parameter) to be able to distuingishg between the fehlerhaft information for part, component, and vehicle!)*)

```{r,results='markup'}
t02_affected_components <- t02_affected %>%
  select(ID_T02) %>%
  left_join(bestand_k1be1,by=c("ID_T02" = "ID_T2")) %>%
  left_join(bestand_k1be2,by=c("ID_T02" = "ID_T2")) %>%
  left_join(bestand_k1di1,by=c("ID_T02" = "ID_T2")) %>%
  left_join(bestand_k1di2,by=c("ID_T02" = "ID_T2"))
```

The result is a data frame in which each part is assigned to one component, but the component IDs are in four different columns. These columns can be united and NA-values can be removed.

```{r,results='markup'}
t02_affected_components <- t02_affected_components %>%
  unite("ID_Component", ID_K1BE1, ID_K1BE2, ID_K1DI1, ID_K1DI2, na.rm = TRUE)
```

In the next step, the affected vehicles must be identified. Therefore, the component IDs are joined with the vehicle IDs by using the function left_join.

```{r,results='markup'}
t02_affected_vehicles <- t02_affected_components %>%
  left_join(bestand_fzg_oem1_typ11,by=c("ID_Component" = "ID_Motor")) %>%
  left_join(bestand_fzg_oem1_typ12,by=c("ID_Component" = "ID_Motor"))
```

Afterwards,the two variables of vehcile IDs can be united and the NA-values can be removed, because no row contains information in both ID columns. *maybe show that*

```{r,results='markup'}
t02_affected_vehicles <- t02_affected_vehicles %>%
  unite("ID_Vehicle", ID_Fahrzeug.x, ID_Fahrzeug.y, na.rm = TRUE)
```

Next, the "Fehlerhaft_Datum" must be added to the data frame because it is needed later to determine the time when vehicles were defective. This information can be found in fzg_oem1_typ11 and fzg_oem1_typ12. Before the join, we select the ID column and the Fehlerhaft_Date column of the vehicle data sets because all other varaibles are not necessary.

```{r,results='markup'}
fzg_oem1_typ11 <- fzg_oem1_typ11 %>% select(ID_Fahrzeug, Fehlerhaft_Datum)
fzg_oem1_typ12 <- fzg_oem1_typ12 %>% select(ID_Fahrzeug, Fehlerhaft_Datum)

t02_affected_vehicles <- t02_affected_vehicles %>%
  left_join(fzg_oem1_typ11,by=c("ID_Vehicle" = "ID_Fahrzeug")) %>%
  left_join(fzg_oem1_typ12,by=c("ID_Vehicle" = "ID_Fahrzeug"))
```

The information is in two variables now, one for cars of type 11 and one for cars of type 12. The information can be put together in one variable and the NA values must be removed.

```{r,results='markup'}
t02_affected_vehicles <- t02_affected_vehicles %>%
  unite("Fehlerhaft_Datum", Fehlerhaft_Datum.x, Fehlerhaft_Datum.y, na.rm = TRUE)
```

The IDs formats are changed into factors to be able to check whether each part is assigned to one component and each component to one vehicle. The "Fehlerhaft_Datum" is changed into a date format. Therefore, the the empty strings in "Fehlerhaft_Datum" must be replaced by NAs before the change of format.

```{r,results='markup'}
t02_affected_vehicles <- t02_affected_vehicles %>%
  mutate(Fehlerhaft_Datum = if_else(Fehlerhaft_Datum == "",NA_character_ ,Fehlerhaft_Datum))

t02_affected_vehicles <- t02_affected_vehicles %>%
  mutate(ID_T02 = as.factor(ID_T02)) %>%
  mutate(ID_Component = as.factor(ID_Component)) %>%
  mutate(ID_Vehicle = as.factor(ID_Vehicle)) %>%
  mutate(Fehlerhaft_Datum = as.Date(Fehlerhaft_Datum))
```

Now, the summary of "to2_affected_vehicles" displays this information. It can be seen that all parts were assigned to one component but not all components were assigned to a vehicle.

```{r,results='markup'}
summary(t02_affected_vehicles)
```

The following filter shows the reason. Only the components from dataframes K1BE1 and K1DI1 were used in vehiclesfrom manufacturer OEM1 (*still keep information about parts that were used in K1BE2 and K1DI2 in data frame? They do not concern our manufacturer but they were affetced by T2*).

```{r,results='markup'}
t02_affected_vehicles %>%
  filter(str_detect(ID_Component, "K1BE1|K1DI1")) %>%
  summary()
```

The empty strings in the vehicle IDs can be replaced by NAs and transformed into factors, similar to the other IDs.

```{r,results='markup'}
t02_affected_vehicles <- t02_affected_vehicles %>%
  mutate(ID_Vehicle = as.character((ID_Vehicle)))%>%
  mutate(ID_Vehicle = if_else(ID_Vehicle == "",NA_character_ ,ID_Vehicle)) %>%
  mutate(ID_Vehicle = as.factor(ID_Vehicle))
```

Now, the registration data of the vehicles is added by a left_join and the ID_Vehicle is formatted to a factor again because the join chnaged it to character.

```{r,results='markup'}
t02_affected_vehicles <- t02_affected_vehicles %>%
  left_join(zulassungen, by = c("ID_Vehicle" = "IDNummer")) %>%
  mutate(ID_Vehicle = as.factor(ID_Vehicle))
```

The following filter shows that each affected vehicle was assigned succesfully to a registration.

```{r,results='markup'}
t02_affected_vehicles %>%
  filter(!is.na(ID_Vehicle) & is.na(Gemeinden))
```