---
title: "General tasks Group 65"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, results= 'hide')
```

### Summersemester 2020

## 1.

Import of the needed packages

```{r, message=FALSE}
if(!require("install.load")){
  install.packages("install.load")
}
library('install.load')

install_load("stringr", "data.table", "tidyverse","plotly")
```


### Preparation of the data for the exercise:
1.Import of the datasets: Komponente_K7.csv, Logistics_delay_K7.csv

```{r, results='markup'}
Production <- fread(file="Data/Data/Logistikverzug/Komponente_K7.csv")
head(Production)

Delivery <- fread(file="Data/Data/Logistikverzug/Logistics_delay_K7.csv")
head(Delivery)
```

2. Filter for relevant columns for the analysis

```{r}
Production <- Production[,c("V1","IDNummer","Produktionsdatum")]

Delivery <- Delivery[,c("V1","IDNummer","Wareneingang")]
```




3.Join both datasets by ID number

```{r,results='markup'}
Prod_Deli_join <- Production %>%
  full_join(Delivery,by="IDNummer")
head(Prod_Deli_join)
```

3. Add another colomn with difference between delivery and production date

```{r,results='markup'}
Logistics_delay <- Prod_Deli_join %>%
  mutate(diff=difftime(Wareneingang, Produktionsdatum, units = "days"))
head(Logistics_delay)
```



*How is the logistics delay distributed? Proof your selection by statistical tests and
briefly describe your approach.*





*What is the minimum/maximum time between delivering and receiving goods?*

*Determine the mean of the logistics delay.*

```{r, results='markup'}
abcd <- Logistics_delay %>%
  summarise(mean=mean(diff),max=max(diff),min=min(diff))
head(abcd)
```

*Visualize the distribution in an appropriate way by displaying a histogram and the
density function using the package plotly.*

```{r, results='markup'}
fig <- plot_ly(x=Logistics_delay$diff, type = "histogram", histnorm = "probability")
fig
```

## 2.

*Why does it make sense to store the available data in separate files instead of saving
everything in a huge table? Name at least four benefits. The available tables represent a typical
data base structure. How is it called?*


This data base structure is calles relational data base. The Benefits from this structure, compared to one huge table is that the Data is stored just once, which  eliminates data deduplication and therefor offers a higher accuray. Furthermore the flexibiltiy of higher, because Complex queries are easy for users to perform. another Benefit is that multiple users can access the same database.
Trust: Relational database models are mature and well-understood.

## 3.

*How many of the parts T4 ended up in vehicles registered in the city of Dortmund?*

## 4.

*Which data types do the attributes of the registration table "Zulassungen_aller_Fahrzeuge"
have? Put your answers into a table which is integrated into your Markdown document*

## 5.

*You want to publish your application. Why does it make sense to store the data sets in a
database on a server? Why is it not recommended to store the data sets on your personal
computer? Name at least three points per question.*


## 6.

*On 11 August 2019 there was an accident involving a stolen car produced by your company.
The driver left the scene without a trace. The license plate of the car, which caused the
accident, was faked and the Vehicle Identification Number (VIN) was removed. Since you work
for the Federal Motor Transport Authority, the police asks for your help to find out where the
vehicle with the engine code "K1DI2-103-1031-21" (corresponds to the engine ID number) was
registered.*

